Bulk Semantic Annotation with an Partially Known Knowledge Base

### 2024-11-11 doc/cicm25-sysdesc/sysdesc.tex
renaming

\begin{figure}[ht]\centering
  \includegraphics[width=8cm]{problem}
  \caption{An annotated Learning Object from an AI Lecture}\label{fig:lo}
\end{figure}

@@

\begin{figure}[ht]\centering
  \includegraphics[width=12cm]{state-space}
  \caption{The definition of the term ``state space'' from the domain model}\label{fig:state-space}
\end{figure}

@@

>>>>

\begin{figure}[ht]\centering
  \fbox{\includegraphics[width=8cm]{../img/problem}}
  \caption{An annotated Learning Object from an AI Lecture}\label{fig:lo}
\end{figure}

@@

\begin{figure}[ht]\centering
  \fbox{\includegraphics[width=12cm]{../img/state-space}}
  \caption{The definition of the term ``state space'' from the domain model}\label{fig:state-space}
\end{figure}

@@

The \srf system is a simple command-line tool that creates a database of
symbol-verbalization pairs\ednote{explain that first}, analyzes \sTeX source files and
then steps through all word occurrences in the document that share the stem with a
verbalization in the database. For each such word, the user is presented with an
annotation choice and interactions that allow to fine-tune the wordwise annotation
workflow.

As \srf addresses mostly power-users, the UI of \srf is command-line based, much like the
early \textsf{ispell} system, see
